word lists

### 2021-04-22 analysis/word_lists.Rmd
prep word lists for Susanne

```{r}
md <- betal %>%
  select(-RatperWord, -aoa_german_b_sd)%>%
  full_join(setal%>%  select(german, english,word_freq,familiarity_m, aoa_german_s_m))%>%
  left_join(mor%>%select(english, aoa_mor, aoa_rating_english))%>%
  full_join(letal%>%left_join(clt))%>%
  filter(!is.na(german))%>%
  mutate(aoa_german_comb = ifelse(!is.na(aoa_german_b_m), aoa_german_b_m, 
                           ifelse(!is.na(aoa_german_s_m), aoa_german_s_m, aoa_german_l_m)))%>%
  select(german, word_freq,aoa_german_b_m, aoa_german_s_m, aoa_german_l_m,aoa_german_comb,clt,english,aoa_mor,aoa_rating_english)%>%
  arrange(aoa_german_comb)%>%
  mutate(select = ifelse(clt == "yes", "x", ""), 
         word_freq = as.numeric(word_freq))%>%
  mutate_if(is.numeric, round, digits = 2)
```

>>>>

```{r}
md <- betal %>%
  select(-RatperWord, -aoa_german_b_sd)%>%
  full_join(setal%>%  select(german, english,word_freq,familiarity_m, aoa_german_s_m))%>%
  left_join(mor%>%select(english, aoa_mor, aoa_rating_english))%>%
  full_join(letal%>%left_join(clt))%>%
  filter(!is.na(german))%>%
  mutate(aoa_german_comb = ifelse(!is.na(aoa_german_b_m), aoa_german_b_m, 
                           ifelse(!is.na(aoa_german_s_m), aoa_german_s_m, aoa_german_l_m)))%>%
  select(german, word_freq,aoa_german_comb,clt,english,aoa_mor)%>%
  arrange(aoa_german_comb)%>%
  mutate(select = ifelse(clt == "yes", "x", ""), 
         word_freq = as.numeric(word_freq))%>%
  select(german, select, aoa_german_comb, word_freq, aoa_mor, clt, english)%>%
  mutate_if(is.numeric, round, digits = 2)
```
